---
title: "p8105_hw1_hca2124"
author: "Helene Apollon"
date: "2026-10-07"
output: github_document
---

#Question1
```{r}
library(tidyverse)
```

```{r}
data("penguins", package = "palmerpenguins")
names (penguins)
penguins = janitor::clean_names(penguins)
```

The 'penguins' dataset includes different measurments of penguins and their body parts.
It has 'r nrow(penguins)' rows and 'r ncol(penguins)' columns. 
The mean flipper length is 'r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)'

```{r}
skimr::skim(penguins)
mean(pull(penguins, flipper_length_mm), na.rm = TRUE)
```
```{r}
round(mean(penguins$flipper_length_mm, na.rm = TRUE), 2)
```
The mean flipper_length_mm is 200.92 with standard deviaition of 14.06

```{r}
library(tidyverse)
flipper_bill_plot =
  ggplot(penguins, aes(x = bill_length_mm,
                       y = flipper_length_mm, color = species)) + 
  geom_point() 
flipper_bill_plot 
ggsave("flipper_bill_plot.pdf")
```

#Question2
```{r}
df_penguins <- tibble(
  norm_samp = rnorm(10),
  logical_vector = norm_samp > 0,
  character_vector = c ("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  factor_vec = factor(c("low", "medium", "high", "low", "medium", "high", "low", "medium", "high", "low"))
)
```

```{r}
mean(pull(df_penguins, norm_samp))
mean(pull(df_penguins, logical_vector))
mean(pull(df_penguins, character_vector))
mean(pull(df_penguins, factor_vec))
     
```

The mean for norm_samp and logical_vector worked.
The mean for the character variable does not work as letters cannot be averaged since they are not numeric.
The mean for the factor variable does not work for the same reason, they are not numeric and cannot be averaged.

```{r}
as.numeric(pull(df_penguins, logical_vector))
as.numeric(pull(df_penguins, character_vector))
as.numeric(pull(df_penguins, factor_vec))
```
When applying as.numeric, logical_vector worked because R converts the variables to 1 and 0, which explains the earlier mean of 0.6 as there are six [1]s and four [0]s. The character vector did not work as the letters could not be read as numerical and replaced with NA. The factor vector worked as it gave a numerical value of 1,2,or 3 to each category.






